Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
mcudameme chart

\usepackage{url}% http://ctan.org/pkg/url

@@

OpenStack \cite{OpenStack} is a cloud operating system that provides Infrastructure as a Service (IaaS). 
It is able to control large pools of compute, storage, and networking resources throughout a 
datacenter. All this resources are managed through a dashboard or an API that gives administrators 
control while empowering their users to provision resources through a web interface
or a command-line. 
It supports most available hypervisors and handles provisioning 
and life-cycle management of VMs. 
The OpenStack architecture offers a flexibility to create a custom cloud, with no proprietary hardware
or software requirements and the ability to integrate with legacy systems and third party technologies.

From the HPC perspective, OpenStack offers high performance computing (HPC) configurations using
multiple supported hypervisors and different hardware architectures. However, despite to be able to
specify some extra parameters for special resources like GPUs, choosing a host based on the existence
of a GPU is currently unsupported in OpenStack \cite{OpenStackGPU}.

@@

The first of them was {\tt MonteCarloMultigpu} from NVIDIA SDK, launched with the default configuration ``scaling=weak'' which adjust the size of the problem depending on the number of accelerators.
The Figure~\ref{fig:mont-opt} depicts the options per second calculated by the application running on the scenarios of Figure~\ref{fig:aws} and on the instances with local GPUs. 
We have removed the results of the Scenario~\ref{subfig:aws2} for clarity ought to they are exactly the same that the obtained from Scenario~\ref{subfig:aws3} up to 8 GPUs. 
In other words, we could state that the results until the 8th GPU would correspond to the Scenario~\ref{subfig:aws2} and thereafter to the Scenario~\ref{subfig:aws3}.
Hence, in this particular case, rCUDA (using remote GPUs) is performing better than CUDA (with its local GPUs) due to rCUDA loads the libraries when its daemon starts.
However, even with rCUDA we can see differences in the results between booth scenarios. We determined that the Scenario~\ref{subfig:aws1} could increase the throughput because
unlike the other setups the GPUs are not sharing the PCI bus with other devices, as it happens in the 4-GPU instances.
% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=\linewidth]{images/aws-mont2.png}
%   \caption{Montecarlo execution time}
%   \label{fig:mont-exe}
% \end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont1.png}
  \caption{NVIDIA SDK {\tt MonteCarloMultiGPU} execution using local and remote GPUs.}
  \label{fig:mont-opt}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.5\textwidth]{images/chart.jpg}
  \caption{Execution time of MCUDA-MEME.}
  \label{fig3}
\end{figure}

@@

\section*{\uppercase{Acknowledgements}}
The authors would like to thank the IT members of the department Vicente Roca and Gustavo Edo for their help.
The researchers were supported by Universitat Jaume I research project (P11B2013-21), project
TIN2011-23283 and~FEDER.

>>>>

\usepackage{url}% http://ctan.org/pkg/url
\usepackage{flushend}

@@

OpenStack is a cloud operating system that provides Infrastructure as a Service (IaaS). 
It is able to control large pools of compute, storage, and networking resources throughout a 
datacenter. All this resources are managed through a dashboard or an API that gives administrators 
control while empowering their users to provision resources through a web interface
or a command-line. 
It supports most available hypervisors and handles provisioning 
and life-cycle management of VMs.

@@

The first of them was {\tt MonteCarloMultigpu} from NVIDIA SDK, launched with the default configuration ``scaling=weak'' which adjust the size of the problem depending on the number of accelerators.
The Figure~\ref{fig:mont-opt} depicts the options per second calculated by the application running on the scenarios of Figure~\ref{fig:aws} and on the instances with local GPUs. 
We have removed the results of the Scenario~\ref{subfig:aws2} for clarity ought to they are exactly the same that the obtained from Scenario~\ref{subfig:aws3} up to 8 GPUs. 
In other words, we could state that the results until the 8th GPU would correspond to the Scenario~\ref{subfig:aws2} and thereafter to the Scenario~\ref{subfig:aws3}.
Hence, in this particular case, rCUDA (using remote GPUs) is performing better than CUDA (with its local GPUs) due to rCUDA loads the libraries when its daemon starts.
However, even with rCUDA we can see differences in the results between booth scenarios. We determined that the Scenario~\ref{subfig:aws1} could increase the throughput because
unlike the other setups the GPUs are not sharing the PCI bus with other devices, as it happens in the 4-GPU instances.
% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=\linewidth]{images/aws-mont2.png}
%   \caption{Montecarlo execution time}
%   \label{fig:mont-exe}
% \end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/mont.pdf}
  \caption{NVIDIA SDK {\tt MonteCarloMultiGPU} execution using local and remote GPUs.}
  \label{fig:mont-opt}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/mcudameme-os.pdf}
  \caption{Scalability results of executing MCUDAMEME with a different number of MPI processes}
  \label{fig3}
\end{figure}

@@

\section*{\uppercase{Acknowledgements}}
The authors would like to thank the IT members of the department Vicente Roca and Gustavo Edo for their help.

The researchers were supported by Universitat Jaume I research project (P11B2013-21), project
TIN2011-23283 and~FEDER.
